Think deep for reef resilience

### 2025-08-06 paper/paper_draft.qmd
Add plotting of a GBR-wide DHW figure for methods section before results

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the IPCC assessed likely range, and GCM development families. The IPCC defines ECS as the
long term warming caused by a doubling of carbon dioxide above its pre-industrial
concentration [@forster2021]. The five GCMs therefore allow for a range of possible climate
futures to be explored, capturing the uncertainty in future responses to CO2 increases
(@sfig-ecs; [@grose2023; @shepherd2018]).

@@

\[**TI: Needs a figure showing DHW trajectories for GBR!**\]

@@

```{=html}
<!-- ![Equilibrium Climate Sensitivity (ECS) values in °C for the GCMs selected (point values).
The pink - dashed box represents the high-certainty ‘very likely’ range for ECS values and
the solid red box represents low-certainty ‘likely’ range for ECS values (Forster et al.,
2021).](../outputs/ADRIA_results/HighResCoralStress/figs/ecs_plot.png){#sfig-ecs
width="`{julia} ecs_width`"} -->
```

@@

>>>>

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the IPCC assessed likely range, and GCM development families. The IPCC defines ECS as the
long term warming caused by a doubling of carbon dioxide above its pre-industrial
concentration [@forster2021]. The five GCMs therefore allow for a range of possible climate
futures to be explored, capturing the uncertainty in future responses to CO2 increases
(@sfig-ecs; @sfig-methods-dhws; [@grose2023; @shepherd2018]).

@@

@@

@@

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#sfig-methods-dhws
width="14.82cm"}
